\cvsection[4]{Work experience}

\begin{cventries}
    \cventry%
        {Network Intrusion Detection on IoT systems, Building Automation, and critical infrastructures.} % Institute
        {PhD in Cyber Security -- Dept. of Computer Science, TU/e} % Title
        {Eindhoven (NL)} % Location
        {2015--2020} % Date(s)
        {\begin{cvitems}
            \item Collaborated with Forescout/SecurityMatters on multiple articles, addressing real-world industry issues on cyber situational awareness and actionable intrusion detection.
            \item Performed a SCADA network assessment for ASML, along with responsible disclosure of vulnerabilities to ICS-CERT.
            \item Developed network monitoring sensors for the Horizon 2020 CITADEL European project.
            \item Served as lab administrator and instructor for the \emph{Hacker's Hut} course (penetration testing fundamentals).
            \item Practical data science: anomaly detection, Bayesian networks, association rules, explainable machine learning, generalized linear models (GLM).
        \end{cvitems}}

	% \cventry%
    %     {Università degli Studi di Padova}
	% 	{State exam for engineering profession}
	% 	{Padua, IT}
	% 	{2015}
	% 	{}

    \cventry%
        {Modelization and control of power electronics for Vanadium Redox Flow Batteries.}
        {Researcher on Electrochemical Energy Storage -- Dept. of Industrial Engineering, UniPD}
        {Padua (IT)}
        {2014--2015}
        {\begin{cvitems}
            \item Coordinated a small research team to design and model a modular 3kW VRFB prototype and its power supply.
            \item Fully automated the layout configuration and multiphysical modelization steps from any given prototype operating point.
            \item Automated the generation of illustrated LaTeX reports for any given operating point.
        \end{cvitems}}

    \cventry%
        {Technological transfer on power conversion for batteries}
        {Internship on Power Electronics -- Power Control Systems S.r.l.}
        {San Vendemiano (IT)}
        {2015}
        {\begin{cvitems}
            \item Performed functional and safety testing on DC/DC converters for batteries.
            \item Built a portable potentiostat for electrocatalysis and cyclic voltammetry.
        \end{cvitems}}

    \cventry%
        {Construction and characterization of a Vanadium Redox Flow Battery prototype cell}
        {Internship on Electrochemistry -- Dept. of Chemical Sciences, UniPD}
        {Padua (IT)}
        {2013--2014}
        {\begin{cvitems}
            \item Synthetized and prepared liquid electrolytes, electrodes, cation exchange membranes.
            \item Assembled, connected, and tested a state of the art VRFB prototype cell.
        \end{cvitems}}

    \cventry%
        {Development of PLC logic and HMI panel for a co-generation biomass power plant}
        {Internship on Industrial Automation -- Teletronic S.r.l.}
        {Vigonza (IT)}
        {2008}
        {\begin{cvitems}
            \item Designed and implemented a novel ``key-value'' solution to update alarm thresholds.
            \item Fully implemented a PID controller for a Siemens Step7 PLC.
            \item Trained other structured personnel on PLC programming.
        \end{cvitems}}

\end{cventries}
